PeakNet: An Autonomous Bragg Peak Finder with Deep Neural Networks

### 2023-06-28 manuscript.natcomm.tex
Support natcomm submission.

\usepackage{style}      % Custom style
\usepackage{more}
\usepackage{constants}  % Load constants

@@

In recent years, neural network models have emerged as a promising avenue for Bragg peak finding.  BraggNet \citep{sullivanBraggNetIntegratingBragg2019} is the first method that demonstrates proficiency of neural network models, specifically U-Net \citep{ronnebergerUNetConvolutionalNetworks2015}, in accurately segmenting peak pixels, including weak peaks, from background pixels in neutron crystallography data.  Specifically, BraggNet employed simulated peaks to create training datasets, which underwent a number of preprocessing steps, including centering and cropping to a specfic size and adding Poisson noise.  It should be noted that BraggNet works on a single peak at a time within a small 32 by 32 window, which deviates significantly from conventional Bragg peak finding tasks that require extracting peak positions from images typically with hundreds or thousands of pixels along one dimension.  Furthermore, another neural network method for Bragg peak analysis was detailed in the work of BraggNN \citep{liuBraggNNFastXray2021}, emphasizing the refinement of Bragg peak positions without the need for explicit fitting of a profile function, such as the pseudo-Voigt profile.  Likewise, BraggNN works on a single peak at a time within a 11 by 11 window, performing regression to two variables representing the peak position.  To the best of our knowledge, no existing neural network based peak-finding models have demonstrated the ability to detect multiple peaks, which is the primary goal we strive to achieve with \peaknet{}.

@@

% Bibliography
\bibliographystyle{plainnat}
\bibliography{bibliography}

>>>>

%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%% PREFERENCES %%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%
% set margin specifics
\usepackage[a4paper, total={6.5in, 9in}]{geometry}

% set unicode
\usepackage[utf8]{inputenc}

% set indent for paragraph
\setlength{\parindent}{2em}

% set graphics support
\usepackage{graphicx}

% setting line spaceing
\renewcommand{\baselinestretch}{2.0}

% use boldface in latex equation
\usepackage{bm}

% Extra math feature
\usepackage{amssymb}
\usepackage{amsmath}

% Code block
\usepackage{listings}
\lstset{
    basicstyle=\footnotesize\ttfamily,
    breaklines=true,
}

% Set the font for lstinline
\makeatletter
\lstdefinestyle{lststyle}{
  basicstyle=%
    \ttfamily
    \color{black}%
    \lst@ifdisplaystyle\scriptsize\fi
}
\makeatother
\lstset{style=lststyle}

% Color
\usepackage{xcolor}

% A better enumerate tool that allows changing the label of item
% It has compatibility issue with beamer;
\usepackage{enumitem}

% Use emojis
\usepackage{pifont}
\usepackage{wasysym}

% No indent
\setlength{\parindent}{0cm}

% Include picture environment
\usepackage[calc]{picture}

% Include TikZ environment
\usepackage{tikz}
\usepackage{calc}

% Include caption
\usepackage{caption}    % !!! For new document
%% \usepackage{caption2}   % !!! Support old document
\usepackage{float}

% Include natbib
\usepackage{natbib}
%% \setcitestyle{authoryear,round}    % Use authoryear format

% Workaround to display bold font in math mode
% Source: https://tex.stackexchange.com/questions/565069/beamer-bold-math-no-longer-working
\DeclareFontShape{OT1}{cmss}{b}{n}{<->ssub * cmss/bx/n}{}

%% \usepackage{setspace}
%% \doublespacing

% To make multirow tables
\usepackage{multirow}

% Use author blocks
\usepackage{authblk}

\newcommand{\PeakNet}{PeakNet}
\newcommand{\peaknet}{PeakNet}
\newcommand{\psocake}{Psocake}
\newcommand{\etal}{\textit{et al}.}
\newcommand{\beSpecific}[1]{(\colorbox{yellow!30}{#1})}
%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%%

@@

In recent years, neural network models have emerged as a promising avenue for Bragg peak finding.  BraggNet \citep{sullivanBraggNetIntegratingBragg2019} is the first method that demonstrates proficiency of neural network models, specifically U-Net \citep{ronnebergerUNetConvolutionalNetworks2015}, in accurately segmenting peak pixels, including weak peaks, from background pixels in neutron crystallography data.  BraggNet employed simulated peaks to create training datasets, which underwent a number of preprocessing steps, including centering and cropping to a specfic size and adding Poisson noise.  It should be noted that BraggNet works on a single peak at a time within a small 32 by 32 window, which deviates significantly from conventional Bragg peak finding tasks that require extracting peak positions from images typically with hundreds or thousands of pixels along one dimension.  Furthermore, another neural network method for Bragg peak analysis was detailed in the work of BraggNN \citep{liuBraggNNFastXray2021}, emphasizing the refinement of Bragg peak positions without the need for explicit fitting of a profile function, such as the pseudo-Voigt profile.  Likewise, BraggNN works on a single peak at a time within a 11 by 11 window, performing regression to two variables representing the peak position.  To the best of our knowledge, no existing neural network based peak-finding models have demonstrated the ability to detect multiple peaks, which is the primary goal we strive to achieve with \peaknet{}.

@@

\begin{thebibliography}{33}
\providecommand{\natexlab}[1]{#1}
\providecommand{\url}[1]{\texttt{#1}}
\expandafter\ifx\csname urlstyle\endcsname\relax
  \providecommand{\doi}[1]{doi: #1}\else
  \providecommand{\doi}{doi: \begingroup \urlstyle{rm}\Url}\fi

\bibitem[Allahgholi et~al.(2019)Allahgholi, Becker, Delfs, Dinapoli,
  Goettlicher, Greiffenberg, Henrich, Hirsemann, Kuhn, Klanner, Klyuev,
  Krueger, Lange, Laurus, Marras, Mezza, Mozzanica, Niemann, Poehlsen,
  Schwandt, Sheviakov, Shi, Smoljanin, Steffen, {Sztuk-Dambietz}, Trunk, Xia,
  Zeribi, Zhang, Zimmer, Schmitt, and
  Graafsma]{allahgholiAdaptiveGainIntegrating2019}
Aschkan Allahgholi, Julian Becker, Annette Delfs, Roberto Dinapoli, Peter
  Goettlicher, Dominic Greiffenberg, Beat Henrich, Helmut Hirsemann, Manuela
  Kuhn, Robert Klanner, Alexander Klyuev, Hans Krueger, Sabine Lange, Torsten
  Laurus, Alessandro Marras, Davide Mezza, Aldo Mozzanica, Magdalena Niemann,
  Jennifer Poehlsen, Joern Schwandt, Igor Sheviakov, Xintian Shi, Sergej
  Smoljanin, Lothar Steffen, Jolanta {Sztuk-Dambietz}, Ulrich Trunk, Qingqing
  Xia, Mourad Zeribi, Jiaguo Zhang, Manfred Zimmer, Bernd Schmitt, and Heinz
  Graafsma.
\newblock The {{Adaptive Gain Integrating Pixel Detector}} at the {{European
  XFEL}}.
\newblock \emph{Journal of Synchrotron Radiation}, 26\penalty0 (1):\penalty0
  74--82, January 2019.
\newblock ISSN 1600-5775.
\newblock \doi{10.1107/S1600577518016077}.

\bibitem[Aquila et~al.(2012)Aquila, Hunter, Doak, Kirian, Fromme, White,
  Andreasson, Arnlund, Bajt, Barends, Barthelmess, Bogan, Bostedt, Bottin,
  Bozek, Caleman, Coppola, Davidsson, DePonte, Elser, Epp, Erk, Fleckenstein,
  Foucar, Frank, Fromme, Graafsma, Grotjohann, Gumprecht, Hajdu, Hampton,
  Hartmann, Hartmann, {Hau-Riege}, Hauser, Hirsemann, Holl, Holton, H{\"o}mke,
  Johansson, Kimmel, Kassemeyer, Krasniqi, K{\"u}hnel, Liang, Lomb, Malmerberg,
  Marchesini, Martin, Maia, Messerschmidt, Nass, Reich, Neutze, Rolles, Rudek,
  Rudenko, Schlichting, Schmidt, Schmidt, Schulz, Seibert, Shoeman, Sierra,
  Soltau, Starodub, Stellato, Stern, Str{\"u}der, Timneanu, Ullrich, Wang,
  Williams, Weidenspointner, Weierstall, Wunderer, Barty, Spence, and
  Chapman]{aquilaTimeresolvedProteinNanocrystallography2012}
Andrew Aquila, Mark~S. Hunter, R.~Bruce Doak, Richard~A. Kirian, Petra Fromme,
  Thomas~A. White, Jakob Andreasson, David Arnlund, Sa{\v s}a Bajt, Thomas
  R.~M. Barends, Miriam Barthelmess, Michael~J. Bogan, Christoph Bostedt,
  Herv{\'e} Bottin, John~D. Bozek, Carl Caleman, Nicola Coppola, Jan Davidsson,
  Daniel~P. DePonte, Veit Elser, Sascha~W. Epp, Benjamin Erk, Holger
  Fleckenstein, Lutz Foucar, Matthias Frank, Raimund Fromme, Heinz Graafsma,
  Ingo Grotjohann, Lars Gumprecht, Janos Hajdu, Christina~Y. Hampton, Andreas
  Hartmann, Robert Hartmann, Stefan {Hau-Riege}, G{\"u}nter Hauser, Helmut
  Hirsemann, Peter Holl, James~M. Holton, Andr{\'e} H{\"o}mke, Linda Johansson,
  Nils Kimmel, Stephan Kassemeyer, Faton Krasniqi, Kai-Uwe K{\"u}hnel, Mengning
  Liang, Lukas Lomb, Erik Malmerberg, Stefano Marchesini, Andrew~V. Martin,
  Filipe~R.N.C. Maia, Marc Messerschmidt, Karol Nass, Christian Reich, Richard
  Neutze, Daniel Rolles, Benedikt Rudek, Artem Rudenko, Ilme Schlichting, Carlo
  Schmidt, Kevin~E. Schmidt, Joachim Schulz, M.~Marvin Seibert, Robert~L.
  Shoeman, Raymond Sierra, Heike Soltau, Dmitri Starodub, Francesco Stellato,
  Stephan Stern, Lothar Str{\"u}der, Nicusor Timneanu, Joachim Ullrich, Xiaoyu
  Wang, Garth~J. Williams, Georg Weidenspointner, Uwe Weierstall, Cornelia
  Wunderer, Anton Barty, John C.~H. Spence, and Henry~N. Chapman.
\newblock Time-resolved protein nanocrystallography using an {{X-ray}}
  free-electron laser.
\newblock \emph{Optics Express}, 20\penalty0 (3):\penalty0 2706, January 2012.
\newblock ISSN 1094-4087.
\newblock \doi{10.1364/OE.20.002706}.

\bibitem[Barty et~al.(2014)Barty, Kirian, Maia, Hantke, Yoon, White, and
  Chapman]{bartyCheetahSoftwareHighthroughput2014}
Anton Barty, Richard~A. Kirian, Filipe R. N.~C. Maia, Max Hantke, Chun~Hong
  Yoon, Thomas~A. White, and Henry Chapman.
\newblock {\emph{Cheetah}} : Software for high-throughput reduction and
  analysis of serial femtosecond {{X-ray}} diffraction data.
\newblock \emph{Journal of Applied Crystallography}, 47\penalty0 (3):\penalty0
  1118--1131, June 2014.
\newblock ISSN 1600-5767.
\newblock \doi{10.1107/S1600576714007626}.

\bibitem[Bolotovsky et~al.(1995)Bolotovsky, White, Darovsky, and
  Coppens]{bolotovskySeedSkewnessMethodIntegration1995}
R.~Bolotovsky, M.~A. White, A.~Darovsky, and P.~Coppens.
\newblock The `{{Seed-Skewness}}' {{Method}} for {{Integration}} of {{Peaks}}
  on {{Imaging Plates}}.
\newblock \emph{Journal of Applied Crystallography}, 28\penalty0 (2):\penalty0
  86--95, April 1995.
\newblock ISSN 0021-8898.
\newblock \doi{10.1107/S0021889894009696}.

\bibitem[Chapman et~al.(2006)Chapman, Barty, Bogan, Boutet, Frank, {Hau-Riege},
  Marchesini, Woods, Bajt, Benner, London, Pl{\"o}njes, Kuhlmann, Treusch,
  D{\"u}sterer, Tschentscher, Schneider, Spiller, M{\"o}ller, Bostedt, Hoener,
  Shapiro, Hodgson, {van der Spoel}, Burmeister, Bergh, Caleman, Huldt,
  Seibert, Maia, Lee, Sz{\"o}ke, Timneanu, and
  Hajdu]{chapmanFemtosecondDiffractiveImaging2006}
Henry~N. Chapman, Anton Barty, Michael~J. Bogan, S{\'e}bastien Boutet, Matthias
  Frank, Stefan~P. {Hau-Riege}, Stefano Marchesini, Bruce~W. Woods, Sa{\v s}a
  Bajt, W.~Henry Benner, Richard~A. London, Elke Pl{\"o}njes, Marion Kuhlmann,
  Rolf Treusch, Stefan D{\"u}sterer, Thomas Tschentscher, Jochen~R. Schneider,
  Eberhard Spiller, Thomas M{\"o}ller, Christoph Bostedt, Matthias Hoener,
  David~A. Shapiro, Keith~O. Hodgson, David {van der Spoel}, Florian
  Burmeister, Magnus Bergh, Carl Caleman, G{\"o}sta Huldt, M.~Marvin Seibert,
  Filipe R. N.~C. Maia, Richard~W. Lee, Abraham Sz{\"o}ke, Nicusor Timneanu,
  and Janos Hajdu.
\newblock Femtosecond diffractive imaging with a soft-{{X-ray}} free-electron
  laser.
\newblock \emph{Nature Physics}, 2\penalty0 (12):\penalty0 839--843, December
  2006.
\newblock ISSN 1745-2473, 1745-2481.
\newblock \doi{10.1038/nphys461}.

\bibitem[Chapman et~al.(2011)Chapman, Fromme, Barty, White, Kirian, Aquila,
  Hunter, Schulz, DePonte, Weierstall, Doak, Maia, Martin, Schlichting, Lomb,
  Coppola, Shoeman, Epp, Hartmann, Rolles, Rudenko, Foucar, Kimmel,
  Weidenspointner, Holl, Liang, Barthelmess, Caleman, Boutet, Bogan,
  Krzywinski, Bostedt, Bajt, Gumprecht, Rudek, Erk, Schmidt, H{\"o}mke, Reich,
  Pietschner, Str{\"u}der, Hauser, Gorke, Ullrich, Herrmann, Schaller,
  Schopper, Soltau, K{\"u}hnel, Messerschmidt, Bozek, {Hau-Riege}, Frank,
  Hampton, Sierra, Starodub, Williams, Hajdu, Timneanu, Seibert, Andreasson,
  Rocker, J{\"o}nsson, Svenda, Stern, Nass, Andritschke, Schr{\"o}ter,
  Krasniqi, Bott, Schmidt, Wang, Grotjohann, Holton, Barends, Neutze,
  Marchesini, Fromme, Schorb, Rupp, Adolph, Gorkhover, Andersson, Hirsemann,
  Potdevin, Graafsma, Nilsson, and Spence]{chapmanFemtosecondXrayProtein2011}
Henry~N. Chapman, Petra Fromme, Anton Barty, Thomas~A. White, Richard~A.
  Kirian, Andrew Aquila, Mark~S. Hunter, Joachim Schulz, Daniel~P. DePonte, Uwe
  Weierstall, R.~Bruce Doak, Filipe R. N.~C. Maia, Andrew~V. Martin, Ilme
  Schlichting, Lukas Lomb, Nicola Coppola, Robert~L. Shoeman, Sascha~W. Epp,
  Robert Hartmann, Daniel Rolles, Artem Rudenko, Lutz Foucar, Nils Kimmel,
  Georg Weidenspointner, Peter Holl, Mengning Liang, Miriam Barthelmess, Carl
  Caleman, S{\'e}bastien Boutet, Michael~J. Bogan, Jacek Krzywinski, Christoph
  Bostedt, Sa{\v s}a Bajt, Lars Gumprecht, Benedikt Rudek, Benjamin Erk, Carlo
  Schmidt, Andr{\'e} H{\"o}mke, Christian Reich, Daniel Pietschner, Lothar
  Str{\"u}der, G{\"u}nter Hauser, Hubert Gorke, Joachim Ullrich, Sven Herrmann,
  Gerhard Schaller, Florian Schopper, Heike Soltau, Kai-Uwe K{\"u}hnel, Marc
  Messerschmidt, John~D. Bozek, Stefan~P. {Hau-Riege}, Matthias Frank,
  Christina~Y. Hampton, Raymond~G. Sierra, Dmitri Starodub, Garth~J. Williams,
  Janos Hajdu, Nicusor Timneanu, M.~Marvin Seibert, Jakob Andreasson, Andrea
  Rocker, Olof J{\"o}nsson, Martin Svenda, Stephan Stern, Karol Nass, Robert
  Andritschke, Claus-Dieter Schr{\"o}ter, Faton Krasniqi, Mario Bott, Kevin~E.
  Schmidt, Xiaoyu Wang, Ingo Grotjohann, James~M. Holton, Thomas R.~M. Barends,
  Richard Neutze, Stefano Marchesini, Raimund Fromme, Sebastian Schorb, Daniela
  Rupp, Marcus Adolph, Tais Gorkhover, Inger Andersson, Helmut Hirsemann,
  Guillaume Potdevin, Heinz Graafsma, Bj{\"o}rn Nilsson, and John C.~H. Spence.
\newblock Femtosecond {{X-ray}} protein nanocrystallography.
\newblock \emph{Nature}, 470\penalty0 (7332):\penalty0 73--77, February 2011.
\newblock ISSN 0028-0836, 1476-4687.
\newblock \doi{10.1038/nature09750}.

\bibitem[{Hadian-Jazi} et~al.(2017){Hadian-Jazi}, Messerschmidt, Darmanin,
  Giewekemeyer, Mancuso, and Abbey]{hadian-jaziPeakfindingAlgorithmBased2017}
Marjan {Hadian-Jazi}, Marc Messerschmidt, Connie Darmanin, Klaus Giewekemeyer,
  Adrian~P. Mancuso, and Brian Abbey.
\newblock A peak-finding algorithm based on robust statistical analysis in
  serial crystallography.
\newblock \emph{Journal of Applied Crystallography}, 50\penalty0 (6):\penalty0
  1705--1715, December 2017.
\newblock ISSN 1600-5767.
\newblock \doi{10.1107/S1600576717014340}.

\bibitem[{Hadian-Jazi} et~al.(2021){Hadian-Jazi}, Sadri, Barty, Yefanov,
  Galchenkova, Oberthuer, Komadina, Brehm, Kirkwood, Mills, {de Wijn}, Letrun,
  Kloos, Vakili, Gelisio, Darmanin, Mancuso, Chapman, and
  Abbey]{hadian-jaziDataReductionSerial2021}
Marjan {Hadian-Jazi}, Alireza Sadri, Anton Barty, Oleksandr Yefanov, Marina
  Galchenkova, Dominik Oberthuer, Dana Komadina, Wolfgang Brehm, Henry
  Kirkwood, Grant Mills, Raphael {de Wijn}, Romain Letrun, Marco Kloos,
  Mohammad Vakili, Luca Gelisio, Connie Darmanin, Adrian~P. Mancuso, Henry~N.
  Chapman, and Brian Abbey.
\newblock Data reduction for serial crystallography using a robust peak finder.
\newblock \emph{Journal of Applied Crystallography}, 54\penalty0 (5):\penalty0
  1360--1378, October 2021.
\newblock ISSN 1600-5767.
\newblock \doi{10.1107/S1600576721007317}.

\bibitem[He et~al.(2016)He, Zhang, Ren, and Sun]{heDeepResidualLearning2016}
Kaiming He, Xiangyu Zhang, Shaoqing Ren, and Jian Sun.
\newblock Deep {{Residual Learning}} for {{Image Recognition}}.
\newblock In \emph{2016 {{IEEE Conference}} on {{Computer Vision}} and
  {{Pattern Recognition}} ({{CVPR}})}, pages 770--778, {Las Vegas, NV, USA},
  June 2016. {IEEE}.
\newblock ISBN 978-1-4673-8851-1.
\newblock \doi{10.1109/CVPR.2016.90}.

\bibitem[Ibrahim et~al.(2020)Ibrahim, Fransson, Chatterjee, Cheah, Hussein,
  Lassalle, Sutherlin, Young, Fuller, Gul, Kim, Simon, {de Lichtenberg},
  Chernev, Bogacz, Pham, Orville, Saichek, Northen, Batyuk, Carbajo,
  {Alonso-Mori}, Tono, Owada, Bhowmick, Bolotovsky, Mendez, Moriarty, Holton,
  Dobbek, Brewster, Adams, Sauter, Bergmann, Zouni, Messinger, Kern, Yachandra,
  and Yano]{ibrahimUntanglingSequenceEvents2020}
Mohamed Ibrahim, Thomas Fransson, Ruchira Chatterjee, Mun~Hon Cheah, Rana
  Hussein, Louise Lassalle, Kyle~D. Sutherlin, Iris~D. Young, Franklin~D.
  Fuller, Sheraz Gul, In-Sik Kim, Philipp~S. Simon, Casper {de Lichtenberg},
  Petko Chernev, Isabel Bogacz, Cindy~C. Pham, Allen~M. Orville, Nicholas
  Saichek, Trent Northen, Alexander Batyuk, Sergio Carbajo, Roberto
  {Alonso-Mori}, Kensuke Tono, Shigeki Owada, Asmit Bhowmick, Robert
  Bolotovsky, Derek Mendez, Nigel~W. Moriarty, James~M. Holton, Holger Dobbek,
  Aaron~S. Brewster, Paul~D. Adams, Nicholas~K. Sauter, Uwe Bergmann, Athina
  Zouni, Johannes Messinger, Jan Kern, Vittal~K. Yachandra, and Junko Yano.
\newblock Untangling the sequence of events during the {{S}}
  {\textsubscript{2}} \textrightarrow{} {{S}} {\textsubscript{3}} transition in
  photosystem {{II}} and implications for the water oxidation mechanism.
\newblock \emph{Proceedings of the National Academy of Sciences}, 117\penalty0
  (23):\penalty0 12624--12635, June 2020.
\newblock ISSN 0027-8424, 1091-6490.
\newblock \doi{10.1073/pnas.2000529117}.

\bibitem[Ke et~al.(2018)Ke, Brewster, Yu, Ushizima, Yang, and
  Sauter]{keConvolutionalNeuralNetworkbased2018}
Tsung-Wei Ke, Aaron~S. Brewster, Stella~X. Yu, Daniela Ushizima, Chao Yang, and
  Nicholas~K. Sauter.
\newblock A convolutional neural network-based screening tool for {{X-ray}}
  serial crystallography.
\newblock \emph{Journal of Synchrotron Radiation}, 25\penalty0 (3):\penalty0
  655--670, May 2018.
\newblock ISSN 1600-5775.
\newblock \doi{10.1107/S1600577518004873}.

\bibitem[Kern et~al.(2018)Kern, Chatterjee, Young, Fuller, Lassalle, Ibrahim,
  Gul, Fransson, Brewster, {Alonso-Mori}, Hussein, Zhang, Douthit, {de
  Lichtenberg}, Cheah, Shevela, Wersig, Seuffert, Sokaras, Pastor, Weninger,
  Kroll, Sierra, Aller, Butryn, Orville, Liang, Batyuk, Koglin, Carbajo,
  Boutet, Moriarty, Holton, Dobbek, Adams, Bergmann, Sauter, Zouni, Messinger,
  Yano, and Yachandra]{kernStructuresIntermediatesKok2018}
Jan Kern, Ruchira Chatterjee, Iris~D. Young, Franklin~D. Fuller, Louise
  Lassalle, Mohamed Ibrahim, Sheraz Gul, Thomas Fransson, Aaron~S. Brewster,
  Roberto {Alonso-Mori}, Rana Hussein, Miao Zhang, Lacey Douthit, Casper {de
  Lichtenberg}, Mun~Hon Cheah, Dmitry Shevela, Julia Wersig, Ina Seuffert,
  Dimosthenis Sokaras, Ernest Pastor, Clemens Weninger, Thomas Kroll,
  Raymond~G. Sierra, Pierre Aller, Agata Butryn, Allen~M. Orville, Mengning
  Liang, Alexander Batyuk, Jason~E. Koglin, Sergio Carbajo, S{\'e}bastien
  Boutet, Nigel~W. Moriarty, James~M. Holton, Holger Dobbek, Paul~D. Adams, Uwe
  Bergmann, Nicholas~K. Sauter, Athina Zouni, Johannes Messinger, Junko Yano,
  and Vittal~K. Yachandra.
\newblock Structures of the intermediates of {{Kok}}'s photosynthetic water
  oxidation clock.
\newblock \emph{Nature}, 563\penalty0 (7731):\penalty0 421--425, November 2018.
\newblock ISSN 0028-0836, 1476-4687.
\newblock \doi{10.1038/s41586-018-0681-2}.

\bibitem[Kupitz et~al.(2014)Kupitz, Basu, Grotjohann, Fromme, Zatsepin, Rendek,
  Hunter, Shoeman, White, Wang, James, Yang, Cobb, Reeder, Sierra, Liu, Barty,
  Aquila, Deponte, Kirian, Bari, Bergkamp, Beyerlein, Bogan, Caleman, Chao,
  Conrad, Davis, Fleckenstein, Galli, {Hau-Riege}, Kassemeyer, Laksmono, Liang,
  Lomb, Marchesini, Martin, Messerschmidt, Milathianaki, Nass, Ros,
  {Roy-Chowdhury}, Schmidt, Seibert, Steinbrener, Stellato, Yan, Yoon, Moore,
  Moore, Pushkar, Williams, Boutet, Doak, Weierstall, Frank, Chapman, Spence,
  and Fromme]{kupitzSerialTimeresolvedCrystallography2014}
Christopher Kupitz, Shibom Basu, Ingo Grotjohann, Raimund Fromme, Nadia~A.
  Zatsepin, Kimberly~N. Rendek, Mark~S. Hunter, Robert~L. Shoeman, Thomas~A.
  White, Dingjie Wang, Daniel James, Jay-How Yang, Danielle~E. Cobb, Brenda
  Reeder, Raymond~G. Sierra, Haiguang Liu, Anton Barty, Andrew~L. Aquila,
  Daniel Deponte, Richard~A. Kirian, Sadia Bari, Jesse~J. Bergkamp, Kenneth~R.
  Beyerlein, Michael~J. Bogan, Carl Caleman, Tzu-Chiao Chao, Chelsie~E. Conrad,
  Katherine~M. Davis, Holger Fleckenstein, Lorenzo Galli, Stefan~P.
  {Hau-Riege}, Stephan Kassemeyer, Hartawan Laksmono, Mengning Liang, Lukas
  Lomb, Stefano Marchesini, Andrew~V. Martin, Marc Messerschmidt, Despina
  Milathianaki, Karol Nass, Alexandra Ros, Shatabdi {Roy-Chowdhury}, Kevin
  Schmidt, Marvin Seibert, Jan Steinbrener, Francesco Stellato, Lifen Yan,
  Chunhong Yoon, Thomas~A. Moore, Ana~L. Moore, Yulia Pushkar, Garth~J.
  Williams, S{\'e}bastien Boutet, R.~Bruce Doak, Uwe Weierstall, Matthias
  Frank, Henry~N. Chapman, John C.~H. Spence, and Petra Fromme.
\newblock Serial time-resolved crystallography of photosystem {{II}} using a
  femtosecond {{X-ray}} laser.
\newblock \emph{Nature}, 513\penalty0 (7517):\penalty0 261--265, September
  2014.
\newblock ISSN 0028-0836, 1476-4687.
\newblock \doi{10.1038/nature13453}.

\bibitem[Lin et~al.(2017)Lin, Doll{\'a}r, Girshick, He, Hariharan, and
  Belongie]{linFeaturePyramidNetworks2017}
Tsung-Yi Lin, Piotr Doll{\'a}r, Ross Girshick, Kaiming He, Bharath Hariharan,
  and Serge Belongie.
\newblock Feature {{Pyramid Networks}} for {{Object Detection}}, April 2017.

\bibitem[Lin et~al.(2018)Lin, Goyal, Girshick, He, and
  Doll{\'a}r]{linFocalLossDense2018}
Tsung-Yi Lin, Priya Goyal, Ross Girshick, Kaiming He, and Piotr Doll{\'a}r.
\newblock Focal {{Loss}} for {{Dense Object Detection}}, February 2018.

\bibitem[Liu et~al.(2021)Liu, Sharma, Park, Kenesei, Miceli, Almer, Kettimuthu,
  and Foster]{liuBraggNNFastXray2021}
Zhengchun Liu, Hemant Sharma, Jun-Sang Park, Peter Kenesei, Antonino Miceli,
  Jonathan Almer, Rajkumar Kettimuthu, and Ian Foster.
\newblock {{BraggNN}}: {{Fast X-ray Bragg Peak Analysis Using Deep Learning}}.
\newblock \emph{arXiv:2008.08198 [cs, eess]}, June 2021.

\bibitem[Nango et~al.(2016)Nango, Royant, Kubo, Nakane, Wickstrand, Kimura,
  Tanaka, Tono, Song, Tanaka, Arima, Yamashita, Kobayashi, Hosaka, Mizohata,
  Nogly, Sugahara, Nam, Nomura, Shimamura, Im, Fujiwara, Yamanaka, Jeon,
  Nishizawa, Oda, Fukuda, Andersson, B{\aa}th, Dods, Davidsson, Matsuoka,
  Kawatake, Murata, Nureki, Owada, Kameshima, Hatsui, Joti, Schertler, Yabashi,
  Bondar, Standfuss, Neutze, and
  Iwata]{nangoThreedimensionalMovieStructural2016}
Eriko Nango, Antoine Royant, Minoru Kubo, Takanori Nakane, Cecilia Wickstrand,
  Tetsunari Kimura, Tomoyuki Tanaka, Kensuke Tono, Changyong Song, Rie Tanaka,
  Toshi Arima, Ayumi Yamashita, Jun Kobayashi, Toshiaki Hosaka, Eiichi
  Mizohata, Przemyslaw Nogly, Michihiro Sugahara, Daewoong Nam, Takashi Nomura,
  Tatsuro Shimamura, Dohyun Im, Takaaki Fujiwara, Yasuaki Yamanaka, Byeonghyun
  Jeon, Tomohiro Nishizawa, Kazumasa Oda, Masahiro Fukuda, Rebecka Andersson,
  Petra B{\aa}th, Robert Dods, Jan Davidsson, Shigeru Matsuoka, Satoshi
  Kawatake, Michio Murata, Osamu Nureki, Shigeki Owada, Takashi Kameshima,
  Takaki Hatsui, Yasumasa Joti, Gebhard Schertler, Makina Yabashi, Ana-Nicoleta
  Bondar, J{\"o}rg Standfuss, Richard Neutze, and So~Iwata.
\newblock A three-dimensional movie of structural changes in bacteriorhodopsin.
\newblock \emph{Science}, 354\penalty0 (6319):\penalty0 1552--1557, December
  2016.
\newblock ISSN 0036-8075, 1095-9203.
\newblock \doi{10.1126/science.aah3497}.

\bibitem[Neutze et~al.(2000)Neutze, Wouts, {van der Spoel}, Weckert, and
  Hajdu]{neutzePotentialBiomolecularImaging2000}
Richard Neutze, Remco Wouts, David {van der Spoel}, Edgar Weckert, and Janos
  Hajdu.
\newblock Potential for biomolecular imaging with femtosecond {{X-ray}} pulses.
\newblock \emph{Nature}, 406\penalty0 (6797):\penalty0 752--757, August 2000.
\newblock ISSN 0028-0836, 1476-4687.
\newblock \doi{10.1038/35021099}.

\bibitem[Oktay et~al.(2018)Oktay, Schlemper, Folgoc, Lee, Heinrich, Misawa,
  Mori, McDonagh, Hammerla, Kainz, Glocker, and
  Rueckert]{oktayAttentionUNetLearning2018}
Ozan Oktay, Jo~Schlemper, Loic~Le Folgoc, Matthew Lee, Mattias Heinrich,
  Kazunari Misawa, Kensaku Mori, Steven McDonagh, Nils~Y. Hammerla, Bernhard
  Kainz, Ben Glocker, and Daniel Rueckert.
\newblock Attention {{U-Net}}: {{Learning Where}} to {{Look}} for the
  {{Pancreas}}, May 2018.

\bibitem[Pande et~al.(2016)Pande, Hutchison, Groenhof, Aquila, Robinson,
  Tenboer, Basu, Boutet, DePonte, Liang, White, Zatsepin, Yefanov, Morozov,
  Oberthuer, Gati, Subramanian, James, Zhao, Koralek, Brayshaw, Kupitz, Conrad,
  {Roy-Chowdhury}, Coe, Metz, Xavier, Grant, Koglin, Ketawala, Fromme, {\v
  S}rajer, Henning, Spence, Ourmazd, Schwander, Weierstall, Frank, Fromme,
  Barty, Chapman, Moffat, {van Thor}, and
  Schmidt]{pandeFemtosecondStructuralDynamics2016a}
Kanupriya Pande, Christopher D.~M. Hutchison, Gerrit Groenhof, Andy Aquila,
  Josef~S. Robinson, Jason Tenboer, Shibom Basu, S{\'e}bastien Boutet,
  Daniel~P. DePonte, Mengning Liang, Thomas~A. White, Nadia~A. Zatsepin,
  Oleksandr Yefanov, Dmitry Morozov, Dominik Oberthuer, Cornelius Gati, Ganesh
  Subramanian, Daniel James, Yun Zhao, Jake Koralek, Jennifer Brayshaw,
  Christopher Kupitz, Chelsie Conrad, Shatabdi {Roy-Chowdhury}, Jesse~D. Coe,
  Markus Metz, Paulraj~Lourdu Xavier, Thomas~D. Grant, Jason~E. Koglin, Gihan
  Ketawala, Raimund Fromme, Vukica {\v S}rajer, Robert Henning, John C.~H.
  Spence, Abbas Ourmazd, Peter Schwander, Uwe Weierstall, Matthias Frank, Petra
  Fromme, Anton Barty, Henry~N. Chapman, Keith Moffat, Jasper~J. {van Thor},
  and Marius Schmidt.
\newblock Femtosecond structural dynamics drives the trans/cis isomerization in
  photoactive yellow protein.
\newblock \emph{Science}, 352\penalty0 (6286):\penalty0 725--729, May 2016.
\newblock ISSN 0036-8075, 1095-9203.
\newblock \doi{10.1126/science.aad5081}.

\bibitem[Ronneberger et~al.(2015)Ronneberger, Fischer, and
  Brox]{ronnebergerUNetConvolutionalNetworks2015}
Olaf Ronneberger, Philipp Fischer, and Thomas Brox.
\newblock U-{{Net}}: {{Convolutional Networks}} for {{Biomedical Image
  Segmentation}}.
\newblock \emph{arXiv:1505.04597 [cs]}, May 2015.

\bibitem[Shin et~al.(2018)Shin, Kim, and Yoon]{shinDataAnalysisUsing2018}
Hocheol Shin, Seungnam Kim, and Chun~Hong Yoon.
\newblock Data {{Analysis}} using {{Psocake}} at {{PAL-XFEL}}.
\newblock \emph{Journal of the Korean Physical Society}, 73\penalty0
  (1):\penalty0 16--20, July 2018.
\newblock ISSN 0374-4884, 1976-8524.
\newblock \doi{10.3938/jkps.73.16}.
